better title eventually

### 2015-05-11 cs261n-paper/paper.tex
Link to wrapup blog post.
Default style.
started writing a little bit.

\documentclass{sig-alternate-hotpets15}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

\title{better title eventually}
\numberofauthors{1}
\author{
 \alignauthor Linda N. Lee, David Fifield\\
   \affaddr{University of California, Berkeley, \{lnl, fifield\}@cs.berkeley.edu} \\
   \vspace{0.5em}
   CS261N Final Report, \today
}
\maketitle

@@

\keywords{User Studies, Tor, Anonymity, Censorship, Security}

@@

\section{Results}
Present situations which really were unexpected. 
Also extract the golden quotes and state them here 
to prove points I want to make.

@@

\section{Experiment Design} 
an informed, user-conscientious, user-focused experiment design to target 
narrow sets of basic features which are used for censorship.

\subsection{Methodology}  
Talk about the justification of the setup and the general 
work flow of an experiment session. Address any details up front
about computers, money, people, etc.

\subsection{Censorship Environments} 
Basically a section like the HOTPETS paper section.
I should add details of exact configurations if available.

\subsection{Tasks}
A section like the HOTPETS paper section. 
I  should add details of exact tasks if available.

\subsection{Feedback} 
Talk about the exit survey and what that covers. 
Explain why we want to know what we are asking about. 
And why this matters.

@@

I guess that other literature on general usability applies here too. %so search for it.

@@

>>>>

%\documentclass{article}
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

@@

\title{better title eventually}
\author{Linda N. Lee, David Fifield\\
University of California, Berkeley, \{lnl, fifield\}@cs.berkeley.edu
}
\maketitle

@@

@@

\section{UX sprint} 
Talk about it just enough that it makes a good storyline for the experiment that we 
are proposing a design of. Motivate it a little bit, and tell a story. Then refer to the 
Appendix for additional information.

@@

\section{Experiment Design}

\subsection{WHAT IS THIS}

\noindent {\bfseries Motivation and Background Story} talk about the generalizability of the work, what we aim to find, and what future work this will lead to. Be sure to sketch the storyline of honing in on specific features.

Tor has grown beyond its original purpose as and has 
since become an important Internet circumvention tool.
We specifically examine it usability as a censorship circumvention tool,
an essential facet for adoption and use.  
We focus our analysis on the connection configuration dialog of Tor browser,
as censorship circumvention requires correct transport configurations. %%
This study is aimed at evaluating 
if and how easily users can circumvent censorship using Tor Browser,
isolating specific browser features to study in the process. 
To this end, we will conduct a large-scale user study examining hundreds of users 
on how they navigate Tor's configuration wizard to complete seven browsing tasks 
in three different adversarial settings.

\subsection{Overview}
For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not. We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in. We will also explain what Tor is, and how they can use it if necessary, and ask them to complete the set of tasks. To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in. We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc. We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.

\subsection{Censorship Environment Simulation}
For our experiment, we plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thusly require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in censorship environments
where others do not. Additionally, some of them require additional information (like bridge 
addresses) before they enable the user to successfully circumvent censorship. 
Details of the three censorship environments are below, increasing in 
order of censorship comprehensiveness and, therefore, difficulty to circumvent.

These environments are not meant perfectly to replicate the network environment
in any particular country.  Censorship environments in are complex and volatile, making
the task of replicating a network environment infeasible. More importantly, replicating these
environments is not critical to this experiment. What is required for this experiment are 
environments which would require users to complete similar Tor configuration 
tasks before they are able to circumvent the censorship environment. We set up the following 
abstract simulations which are inspired by reality and require users to complete various tasks
to circumvent censorship.

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{Corporate network.}
A simulation of an enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
outside a small whitelisted set.
\item{Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

\subsection{Web Browsing Tasks}
The tasks below are designed to be easy and quick to complete for an average
computer user. This design is critical since the objective of the experiment is to observe
how comfortable users are with circumventing censorship, which we indirectly measure
by taking data regarding how participants complete the task. Giving participants tasks 
they are not comfortable with performing or sending them to websites which they are 
unfamiliar with will introduce more variables into the experiment to account for. 
Specifically, we would need to separate any confusion caused by the task itself versus
the task of circumventing censorship.

To create a set of tasks that an average user will be able to complete reliably, 
we turned to the top Alexa sites, the most popular websites on the Internet. This 
is an indication of representative and relevant browsing behavior. To reach the final
set of website destinations, we selected sites which were popular, but also commonly
censored around the world to make our study more representative. The tasks 
associated with each website were crafted with user familiarity in mind but narrowed 
down the possibilities by removing tasks which caused ethical concerns (such as 
requiring a user to log in to a websites, which would reveal login information).  
We believe that these tasks we will use for our study will be simple tasks for an average 
user to complete, on familiar websites.

All participants will be given the same set of tasks, regardless of their simulated
censorship environment.  Although every participant will attempt to complete the same 
set of tasks, the difficulty of completing these tasks will vary based on their chosen environment. 
Depending on the censorship environment, some tasks may not even require the use or Tor Browser.

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Do a Google web search.
\item Watch a YouTube video.
\item Find the Amazon best-selling books.
\item Find Yahoo's exchange rate between dollars and euros.
\item Read the Wikipedia featured article.
\item Find the Twitter trending topics.
\item Find directions on Bing Maps.
\end{itemize}

We plan to present our work at HotPETS2015 and solicit feedback on the design
of this experiment. Circumvention is broader than the stereotypical ``dissident blogger'' 
use case. We will solicit feedback on which additional tasks will provide additional insight,
or if there are different tasks which are representative of other censorship evasion use cases.

\subsection{Methodology}  
We plan to recruit up to 200 users for the purpose of this study, 
making it largest user study to date examining Tor (check this). 
This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops with 
cubicle walls separating each laptop. We will use individual host firewalls to simulate
the censorship environments and will write a browser extension to 
log when user activity, such as what websites they were successfully able to visit. 
The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will take less than an hour. 
Participants will be compensated \$30 for their time, 
which is more to cover minimum wage and transportation costs

\subsection{Data}

\subsubsection{Measurements}
Screen capture, timing, completion, clicks, etc. Things to measure
about the activity.

\subsubsection{Feedback} 
Talk about the exit survey and what that covers. 
Explain why we want to know what we are asking about. 
And why this matters.

@@

I guess that other literature on general usability applies here too. %so search for it. 
Especially look into browser configuration work. %do it to it.

@@

\appendix

\subsection{Motivation}
Talk about why we did what we did, and what the end goal 
of the experiment was. Also talk about how we expected users
to be much better at installing and downloading than they were.

\subsection{Experiment Overview}
Talk about how the experiment was for an average user. We start
with the cognitive walkthrough, then have them do one on a dummy
and calibration task, we give feedback on the walkthrough, and then 
give them the freedom to complete the web tasks.

GET THE LIST OF TASKS WE MADE THEM DO.

\subsection{Methodology}
How we recruited, what the setup was like, how we got the tasks, details of 
how the experiment was run, and things like that.

\subsection{Results}
Present situations which really were unexpected. 
Also extract the golden quotes and state them here 
to prove points I want to make.

\url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}

\subsection{Resources}

Our online artifacts of our completed pilot study, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
\end{itemize}

\noindent Subtitled screen videos:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}
